Mapping malaria by sharing spatial information between incidence and prevalence datasets

### 2019-09-04 ms.tex
Final ros edits.

\begin{figure}
% to be removed before submission
\makebox{\includegraphics[width = 1.1\textwidth]{figures/sen_both_cv12_preds.png}}
\caption{\label{predobsmapsen}
Incidence data and predicted incidence maps.
The incidence data (left), predicted incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted incidence from the joint model for spatially cross-validated out-of-sample polygons (right) for Senegal.
}

@@

\begin{figure}
% to be removed before submission
\makebox{\includegraphics[width = 1.1\textwidth]{figures/mdg_both_cv12_preds.png}}
\caption{\label{predobsmapmdg}Input incidence data and predicted incidence maps.
The incidence data (left), predicted incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted incidence from the joint model for spatially cross-validated out-of-sample polygons (right) for Madagascar.
}

@@

\begin{figure}[h!]
% to be removed before submission
\makebox{\includegraphics[width = 0.8\textwidth]{figures/idn_both_cv12_preds.png}}
\caption{\label{predobsmapidn}
Incidence data and predicted incidence maps.
The incidence data (top), predicted incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Indonesia.
}
\end{figure}

>>>>

\begin{figure}
% to be removed before submission
\makebox{\includegraphics[width = 1.1\textwidth]{figures/sen_both_cv12_preds.png}}
\caption{\label{predobsmapsen}
Reported incidence data and modelled incidence maps for Senegal. 
The adjusted input aggregated data is plotted in Panel A, while Panel B maps the predictions of the prevalence Gaussian Process model for for spatially cross-validated out-of-sample polygons and Panel C maps the predicted incidence from the joint model.
}

@@

\begin{figure}
% to be removed before submission
\makebox{\includegraphics[width = 1.1\textwidth]{figures/mdg_both_cv12_preds.png}}
\caption{\label{predobsmapmdg}
Reported incidence data and modelled incidence maps for Madagascar. 
The adjusted input aggregated data is plotted in Panel A, while Panel B maps the predictions of the prevalence Gaussian Process model for for spatially cross-validated out-of-sample polygons and Panel C maps the predicted incidence from the joint model.
}

@@

\begin{figure}[h!]
% to be removed before submission
\makebox{\includegraphics[width = 0.8\textwidth]{figures/idn_both_cv12_preds.png}}
\caption{\label{predobsmapidn}
Reported incidence data and modelled incidence maps for Indonesia. 
The adjusted input aggregated data is plotted in Panel A, while Panel B maps the predictions of the prevalence Gaussian Process model for for spatially cross-validated out-of-sample polygons and Panel C maps the predicted incidence from the joint model.
}
\end{figure}
